---
title: "p8105_hw1_do2381"
author: "Daniel Ojeranti"
date: "9/13/2020"
output: github_document
---

**This is my solution to HW1**

```{r, include = FALSE}

library( tidyverse)

```
# Problem 1

**Create a data frame with the specified elements.**

```{Create Df, eval = FALSE}

prob1.df = tibble(
  vec.samp = rnorm(10),
  vec.samp.pos = vec.samp > 0,
  vec.char = c("Jordan", "LeBron", "Magic", "Giannis", "Harden", "Westbrook", "Booker", "Trae", "Paul", "Kahwi"),
  vec.fact = factor(c("Great", "Great", "Great", "Good", "Good", "Okay", "Okay", "Good", "Good", "Good"))
)
```

**The mean of each variable.**

```{Mean, eval = FALSE}
mean(pull(prob1.df, vec.samp))
mean(pull(prob1.df, vec.samp.pos))
mean(pull(prob1.df, vec.char))
mean(pull(prob1.df, vec.fact))
```

I get mean values for the vector sample, and the vector sample with the logical expression. I think this is because of the four vectors created, those are the two that held a collection of numerical values. 

**This is each variable as a numeric**

```{As numeric, eval = FALSE}

as.numeric(pull(prob1.df, vec.samp.pos))
as.numeric(pull(prob1.df, vec.char))
as.numeric(pull(prob1.df, vec.fact))
```

When I convert the logical variable, I get 0s and 1s. I think this is due to the conditions set. The "0's" are the values that did not meet the condition where as the "1s" are the values that did. This makes sense as to why R was able to compute the means of the values that met the condition.

When I convert the character variable, I get a bunch of "NA". I think this is because the character variable holds no actual numerical value, hence why they're considered not applicable. It was expected that R was not able to compute a mean.

When I convert the factor variable, I get a collection of 1s 2s and 3s. I think this is because the factor variable was assigned a maximum of 3 levels and the numeric function classify which level each character belonged in.It was expected that R was not able to compute a mean because these numbers were generated by a character "level".



```{SecondChunk, eval = FALSE}

num.samp.pos = as.numeric(pull(prob1.df, vec.samp))
fact.samp.pos = as.factor(pull(prob1.df, vec.samp))
num.fact.num.pos = as.numeric(as.factor(pull(prob1.df, vec.samp)))

```


# Problem 2


```{r, include = FALSE}
data("penguins", package = "palmerpenguins")
summary(penguins)
```

This dataset includes the following variables:

* Species
  * Adelie (152)
  * Chinstrap (68)
  * Gentoo (124)
* Island
  * Biscoe (168)
  * Dream (124)
  * Torgersen (52)
  
* Bill_length_mm ( Mean: `r round(mean(pull(penguins, bill_length_mm), na.rm = TRUE), digits = 2)` , SD: `r round(sd(pull(penguins, bill_length_mm), na.rm = TRUE), digits = 2)` )
* Bill_depth_mm ( Mean: `r round(mean(pull(penguins, bill_depth_mm), na.rm = TRUE),digits = 2)` , SD: `r round(sd(pull(penguins, bill_depth_mm), na.rm = TRUE), digits = 2)` )
* Flipper_length_mm (Mean: `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE),digits = 2)`, SD:`r round(sd(pull(penguins, flipper_length_mm), na.rm = TRUE),digits = 2)`)
* Body_mass_g ( Mean: `r round(mean(pull(penguins, body_mass_g), na.rm = TRUE),digits = 2)` , SD: `r round(sd(pull(penguins, body_mass_g), na.rm = TRUE), digits = 2)` )
* Sex
  * Male (168)
  * Female (165)
* Year ( Mean: `r round(mean(pull(penguins, year), na.rm = TRUE))`)


The penguin dataset has `r nrow(palmerpenguins::penguins)` rows and `r ncol(palmerpenguins::penguins)` columns.

The mean flipper length is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), digits = 2)`.

```{Scatterplot, echo = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + ggtitle("Flipper Length vs. Bill Length")
ggsave("Penguin_Scatter_Plot.pdf")
```



